Modelling the emergence of whisker barrels

### 2020-05-29 paper/briefpaper/brief.tex
Notes about conservation of a

The present results suggest that the key requirements for the emergence of
realistic barrel patterning are i) at each cortical location thalamocortical
projections compete for a limited number of available synaptic connections
(Eqs.~\ref{eq:dc}--\ref{eq:da}), ii) at each location the branching rate of a
given projection is reduced by the density of other projections
(Eq.\,\ref{eq:comp}), and iii) \cmnt{REVIEW: No longer true. Try plotting $a$
  vs $t$} the branch density of each projection is conserved over time.

>>>>

The present results suggest that the key requirements for the emergence of
realistic barrel patterning are i) at each cortical location thalamocortical
projections compete for a limited number of available synaptic connections
(Eqs.~\ref{eq:dc}--\ref{eq:da}), ii) at each location the branching rate of a
given projection is reduced by the density of other projections
(Eq.\,\ref{eq:comp}), and iii) \cmnt{REVIEW: plotting $a(t)$, $c(t)$ and
  $a(t)-c(t)$ showed that there was some leaking of $a$ going on at the
  boundary; increasing the boundary fall off distance to 3 times hex to hex
  distance reduces the leaking to a negligible amount. So the branchdesnity of
each projections IS conserved over time.} the branch density of
each projection is conserved over time.
